---
title: "Perform-Bulk-Reference-Uploads"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview
Once you have finished filling out your input.xlsx file, you are ready to create references on DataStore! It can be quite easy to make hundreds or even thousands of references so if this is the first time you have used this package please consider testing a subset of your input.xlsx file using the development server.

# Testing on the development server

To test your input.xlsx file on the development server, you should consider truncating the input.xlsx file and limiting it to just a few rows (references) to create. Save this truncated version with a new name and pass it to the `generate_references()` function while setting the `dev` parameter to `TRUE`. You will also need to specify which sheet within the .xlxs you want to use to generate references on DataStore:

```{r dev_testing, eval=FALSE}
dev_refs <- generate_references(filename = "truncated_input.xlsx",
                                      path = getwd(),
                                      sheet = "AudioRecording",
                                      dev = TRUE))
```

If the data validation steps in the `generate_references()` function produced any errors, you will have to address those before proceeding. See the [Data Validation Checks](05_Data-Validation-Checks.html) vignette for additional information on these tests and how to fix your input.xlsx file.

Once the function has run, you can look at your draft references on the [DataStore development server](https://irmadev.nps.gov/DataStore/) to make sure everything is copasetic. Make any necessary adjustments to your full input.xlsx file before using it with the `generate_references()` with the `dev` parameter set to `FALSE`.

You may want to check the object `dev_refs` to see a list of the newly created reference numbers, which has been added to the information you supplied in your `truncated_input.xlsx` file.

# Create and activate references already!
Creating references is the easy part! 

Run the following line of code to supply your full (not truncated) input.xlsx file. This will create references, populate reference landing pages, and upload the specified files. It will not activate the references:

```{r DSuploads, eval = FALSE}
new_refs <- generate_references(filename = "DSbulkUplaodR_input.xlsx",
                          path = getwd(),
                          sheet = "AudioRecording",
                          dev = FALSE))
```

Once you are satisfied with the references and/or they have received the appropriate levelof review, you can activate them using the `activate_references` function:

```{r activate_refs, eval = FALSE}
activate_references(reference_id = new_refs$reference_id,
                                   dev = FALSE)
```

Alternatively, if your references don't need additional review and you are sure they are being properly created, you can directly activate them using the `generate_references` function:

```{r DSactivate, eval = FALSE}
active_refs <- generate_references(filename = "DSbulkUplaodR_input.xlsx",
                          path = getwd(),
                          sheet = "AudioRecording",
                          activate_refs = TRUE,
                          dev = FALSE))
```

## Increase file numbers and sizes
For safety's sake, the `generate_references()` function has a setting for the maximum allowable number of files and volume of data that can be uploaded during a single operation. These defaults are 500 files and 10 GB. You can increase the allowable upload file number and size above the default settings by changing those parameters (see the documentation for `generate_references()`). For instance, to increase the maximum file number to 5,000 and the maximum volume of data to 500 GB, you would run the following code:

```{r increase_max, eval = FALSE}
new_refs <- generate_references(filename = "DSbulkUploadR_input.xlsx",
                          path = getwd(),
                          sheet = "AudioRecording",
                          max_file_upload = 5000,
                          max_file_size = 500
                          dev = FALSE))
```

# Save your output
In addition to creating new references on DataStore, the `generate_references()` function will return a dataframe in R (in these examples that dataframe is stored as the object `dev_refs`, `new_refs`, or `active_refs`). This dataframe contains all the information you supplied in your input.txt file and two additional columns: the DataStore reference ID for each new reference created and the status of the new reference (draft/active). 

You may wish to save this file to your current working directory for later use or your personal records:

```{r save_file, eval = FALSE}
readr::write_csv(new_refs,
                 "new_reference_ids.csv")
```
